%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,10pt]{extarticle} % Default font size and paper size

\usepackage{fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin} % Main document font
\fontspec{[FontAwesome.otf]}


\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

% \usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be 
%\usepackage{fullpage}
\usepackage{geometry}
\geometry{a4paper,margin=1.25cm}
%\geometry{a4paper,left=20mm, top=20mm}
 %To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}

\usepackage{hyperref} % Required for adding links	and customizing them
%\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\definecolor{linkcolour}{rgb}{0.3,0.3,0.3} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{0pt}{0pt} % Spacing around sections

\usepackage{multicol}
\setlength{\columnsep}{1cm}

\usepackage{textcomp}

\usepackage{fontawesome}

\begin{document}

\pagestyle{empty} % Removes page numbering

\font\fb=''[cmr10]'' % Change the font of the \LaTeX command under the skills section

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------
\par{\centering{\Huge Himanshu \textsc{Verma}}\par} % Your name
\par{\centering\large {\textsc{Department of Computer Science and Engineering}}\par}\large
\par{\centering\large {\textsc{Undergraduate student at Indian Institute of Technology, Kharagpur}}\par}\large
%\par{{\begin{center}Dual Degree, \emph{Computer Science and Engineering}\end{center}}}
\par{\centering\large {\textsc{A-210, LBS Hall of Residence, IIT Kharagpur, West Bengal - 721302}}\par}\large
%\begin{flushleft}{\normalsize {\href{mailto:nareshmdu@gmail.com}{nareshmdu@gmail.com}}}\end{flushleft}
\hspace{1cm}\normalsize \faEnvelope\ {\href{mailto:vhimanshu.iitkgp@gmail.com}{vhimanshu.iitkgp@gmail.com}}\hfill \normalsize \faGithub\ {\href{https://github.com/himanshuv1996}{himanshuv1996}}\hfill \normalsize \faLinkedinSquare\ {\href{https://www.linkedin.com/in/himanshu-v}{himanshu-v}} \hfill {\faPhone\ +91-8609273495} \hspace{1cm}\vspace{10pt}

\textbf{\large{Company Recruitment Team}} \hfill \textit{February 27, 2017}

\textsc{EdgeVerve Systems} \\
\textsc{Bengaluru, India}\\

\underline{\textbf{Job Application for the role of Software Developer Intern}}

Dear sir or madam,\\

I am Himanshu Verma, currently pursuing my Dual Degree (B.Tech + M.Tech) in Computer Science and Engineering at IIT-Kharagpur. I am devoted to the ﬁeld of Computer Science and have been exploring several ﬁelds over the last couple of years. I interned at Flipkart Internet Pvt. Limited, Bangalore, India in Summer 2016. I've narrowed down my research interests to Natural Language Processing (NLP) and Machine Learning (ML). I am proficient with several front-end and back-end technologies, and open to work on either end of the spectrum. I have expanded my rhetorical skills greatly over the past years thanks to a fair level of public speaking during my internship. \\

I am a conscientious person who believes in hard work and attention to detail. I thoroughly enjoy working with a team, as it helps expand my thinking capabilities and ideas. I’m ﬂexible and usually quick to pick up new skills. Thanks to the brilliant work culture currently installed at EdgeVerve, I believe I will be able to work at maximum efficiency and make more than satisfactory contributions to the project(s) allotted. I would really hope to be able to come to work every day to a place where I knew not only are my technical skills valuable, but my personal philosophies are as well.\\

The reason I believe I would be a perfect fit at EdgeVerve, and vice-versa, is the very fact that the interminable opportunities that EdgeVerve has on offer are the very challenges I am passionate about solving using the technical skills I've acquired. I would constantly seek to collaborate, contribute and learn along the process of achieving the end goal.\\

I look forward to speaking with you in further detail about the internship and opportunity with EdgeVerve. This would be a great opportunity and I strongly believe that if given a chance I will prove myself and contribute to the growth \& success of the company.\\

Sincerely,

\textbf{\large{Himanshu Verma}}\\
Department of Computer Science and Engineering\\
Indian Institute of Technology, Kharagpur\\
West Bengal, India\\

%\itshape{Attached: Curriculum Vitae}

\end{document}